\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-03-01 paper.tex
Commented out L2TOR example, partially rewritten MuMMER description

\section{Application Examples}
\label{application}

\subsection{Application to joint-action situations}

\uwds is used within the European project MuMMER for service robots to compute
visibility and knowledge about objects, places and agents within a mall
environment.

We present here a simplified scenario, yet representative of situations which
are processed in real-time by MuMMER robots: two humans and a robot are looking
at a table and have to coordinate joint actions (pick and place).  One object on
the table (the green box) is only visible to one human and the robot, but hidden
to the second human. The robot needs to take into account this fact to generate
appropriate and legible joint manipulation actions.
Figure~\ref{fig|mummerarchitecture} illustrates the topology of the \uwds
network that we use to this end.

@@

A first client, \textit{env\_provider}, provides the environment models and
allows to build a first \texttt{ENV} world where static objects, furnitures and
walls are present.  Then, three worlds cascade through three (independent)
clients: \textit{robot\_state\_monitor} augments {\tt ENV} with the robot state
(using underneath the ROS robot state publisher node) and broadcast a new world
{\tt ENV\_ROBOTS}. \textit{objects\_monitor} then recognises and adds the
dynamic objects (using {\tt
ar\_track\_alvar}\footnote{\url{http://wiki.ros.org/ar_track_alvar}}).
\textit{object\_monitor} finally detects and adds the humans
(using~\cite{Khalidov_Idiap-RR-02-2017}). It broadcasts a world called {\tt
BASE} that eventually contains the static environment, the robots, the dynamic
objects and the detected humans.

The world \texttt{BASE} goes through a \textit{physics filter} client as
explained in section~\ref{physics} to obtain the \texttt{STABLE} world where all
elements are present with physically-consistent locations. This
physically-correct world is used by the
\textit{computation\_of\_spatial\_relations} client to compute spatial relations
such as {\tt onTop}, {\tt isIn} or {\tt isAbove} (see Section~\ref{spatial}).

The world \texttt{STABLE} is also used by a \textit{perspectives\_filter} client
to compute the different visual perspectives of each agent (in our case: human
1, human 2 and the robot itself). In addition to a 3D rendering of the input
world from the perspective of the agent, it aggregates the history of what was
visible to the agent at a given point in time. As such, it does not only offer a
snapshot of the agent visual perspective at the current time but also act as the
visual memory of each agent.

@@

\uwds makes it possible to implement such a geometric reasoning pipeline in a
fully decoupled way, and each intermediary ``world'' can be easily introspected
at run-time. As such, \uwds facilitates the implementation and debugging of complex
spatio-temporal reasoning pipelines.

@@

We are currently deploying a similar network in the framework of the
European project MuMMER where a Pepper robot handles interactive
situations in a large shopping centre in Finland. One of the situation is a guiding task where
Pepper will help people to find their route by pointing them landmarks and
explaining them how to reach a destination. \uwds effectively facilitates the
implementation of the required robotic architecture where perception and high-level
reasoning (including complex, human-aware reasoning) have to be tightly
integrated, and yet are developed across multiple partners with different
expertise.

@@

\subsection{Application to human-robot interaction and spatial reasoning}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2-blind}
    \caption{A user manipulating objects on top of an RFID mat (providing object
    localisation) with a NAO robot, while an operator monitors
    the interaction on a tablet that displays an {\tt uwds view} client [photo blurred for blind review].}

    \label{fig|l2torexample}
\end{figure}

\uwds is being used within the European L2TOR project~\cite{belpaeme2015l2tor} as part of a system for a large scale study with 150 children. The \uwds {\tt spatial\_relations} module is used to visualise counting tasks and teach spatial words for a second language(l2). The loose coupling provided by \uwds allows for easy integration with the {\tt spatial\_relations} between either an object localisation system that would allow for use in a physical environment (Figure~\ref{fig|l2torexample}) or a virtual tablet game. As well, this loose coupling facilitated development on multiple parts of the software individually across multiple international sites.

In the counting task the child is instructed to move toy animals into enclosures. The {\tt spatial\_relations} module calculates when the robots have been placed in the enclosure, and passes this on to another part of the system. The robot then teaches the children l2 words for the numbers and encourages the children to count along. While teaching the spatial domain the robot ask the children to move objects into positions related to other objects (e.g. put the box on the shelf). The performance can be evaluated by the {\tt spatial\_relations} module between objects. In both tasks the robot is able to provide targeted feedback on the position of an animal or object as the spatial relation is calculated rather than just attempting to fulfil a particular position criteria

%\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor} in order to conceptualise and visualise the spatial relations and visibility of the physical objects that participants interact with. In one of the scenarios of this project, participants are instructed by a NAO robot to manipulate a number of Duplo-like animals on top of a printed background paper which serves as a landscape (Figure~\ref{fig|l2torexample}). The robot instructions are based on pedagogical strategies to promote spatial relation learning by object manipulation. Such instructions include commands to place the elephant \textit{on top} or \textit{next to} the cube, or put the giraffe \textit{inside} the house.  To assess the performance, the robot and the operator need to compute spatial relationships between objects from the visual perspective of the participant.

>>>>

\section{Application Example: Perspective-aware joint actions}
\label{application}

%\subsection{Application to joint-action situations}

\uwds is being used within the large European project
MuMMER\footnote{\url{http://www.mummer-project.eu}} for service robots to
compute visibility and knowledge about objects, places and agents within a mall
environment.

We present here a simplified scenario, yet representative of situations which
are processed in real-time by MuMMER robots: two humans and a robot are looking
at a table and have to coordinate joint actions (pick and place).  One object on
the table (the green box in Figure~\ref{fig|mummerarchitecture}) is only visible
to one human and the robot, but hidden to the second human. The robot needs to
take into account this fact to generate appropriate and legible joint
manipulation actions.  Figure~\ref{fig|mummerarchitecture} illustrates the
topology of the \uwds network that we use to this end.

@@

A first client, \textit{static\_env\_provider}, provides the environment models and
allows to build a first \texttt{ENV} world where static objects, furnitures and
walls are present.  Then, three worlds cascade through three (independent)
clients: \textit{robots\_state\_monitor} augments {\tt ENV} with the robot state
(using underneath the ROS robot state publisher node) and broadcast a new world
{\tt ENV\_ROBOTS}. \textit{objects\_monitor} then recognises and adds the
dynamic objects (using {\tt
ar\_track\_alvar}\footnote{\url{http://wiki.ros.org/ar_track_alvar}}).
\textit{humans\_monitor} finally detects and continuously updates the humans
poses (using~\cite{Khalidov_Idiap-RR-02-2017}). It broadcasts a world called {\tt
BASE} that contains as a result the static environment, the robots, the dynamic
objects and the detected humans.

The world \texttt{BASE} goes through a \textit{physics filter} client (as
explained in section~\ref{physics}) to obtain the \texttt{STABLE} world where all
elements are present with physically-consistent locations. This
physically-correct world is used by the
\textit{computation\_of\_spatial\_relations} client to compute spatial relations
such as {\tt onTop}, {\tt isIn} or {\tt isAbove} (see Section~\ref{spatial}).

The world \texttt{STABLE} is also used by a \textit{perspectives\_filter} client
to compute the different visual perspectives of each agent (in our case: human
1, human 2 and the robot itself). In addition to a 3D rendering of the input
world from the perspective of the agent, it aggregates the history of what was
visible to the agent at a given point in time. As such, it does not only offer a
snapshot of the agent visual perspective at the current time but also acts as the
visual memory of each agent.

@@

\uwds makes it possible to implement such a geometric reasoning pipeline in a
fully decoupled way, and each intermediary world can be easily introspected at
run-time. This example shows how \uwds facilitates the implementation and
debugging of complex spatio-temporal reasoning pipelines.

@@

We are currently deploying a similar network in the framework of the European
project MuMMER where a Pepper robot handles interactive situations in a large
shopping centre in Finland. One of the situation is a guiding task where Pepper
help people to find their route by pointing them landmarks and explaining them
how to reach a destination. To be effevtive, this helping behaviour needs to be
aware of the visual perspective of the human. \uwds facilitates the
implementation of such a spatio-temporal reasoning pipeline, where perception
and high-level reasoning (including complex, human-aware reasoning) have to be
tightly integrated. Because of the decoupling of each of the clients in the
network, \uwds also practically supports software development spread across
multiple partners in different countries, with different expertise.

@@

%\subsection{Application to human-robot interaction and spatial reasoning}
%
%\begin{figure}
%    \centering
%    \includegraphics[width=\linewidth]{l2tor-photo2-blind}
%    \caption{A user manipulating objects on top of an RFID mat (providing object
%    localisation) with a NAO robot, while an operator monitors
%    the interaction on a tablet that displays an {\tt uwds view} client [photo blurred for blind review].}
%
%    \label{fig|l2torexample}
%\end{figure}
%
%\uwds is being used within the European L2TOR project~\cite{belpaeme2015l2tor}
%to implement the symbolic spatial reasoning pipeline of a system used in a large
%scale study (150 children). \uwds supports 
%easy integration with the {\tt spatial\_relations} between either an object
%localisation system that would allow for use in a physical environment
%(Figure~\ref{fig|l2torexample}) or a virtual tablet game. 
%
%The \uwds\xspace {\tt spatial\_relations} module is
%used to visualise counting tasks and teach spatial words for a second language.
%
%In the counting task the child is instructed to move toy animals into
%enclosures. The {\tt spatial\_relations} module calculates when the objects have
%been placed in the enclosure, and passes this on to another part of the system.
%The robot then teaches the children l2 words for the numbers and encourages the
%children to count along. While teaching the spatial domain the robot ask the
%children to move objects into positions related to other objects (\eg put the
%box on the shelf). The performance can be evaluated by the {\tt
%spatial\_relations} module between objects. In both tasks the robot is able to
%provide targeted feedback on the position of an animal or object as the spatial
%relation is calculated rather than just attempting to fulfil a particular
%position criteria
%
%The loose coupling provided by As well, this loose
%coupling facilitated development on multiple parts of the software individually
%across multiple international sites.
%
%%\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor}
%%in order to conceptualise and visualise the spatial relations and visibility of
%%the physical objects that participants interact with. In one of the scenarios
%%of this project, participants are instructed by a NAO robot to manipulate a
%%number of Duplo-like animals on top of a printed background paper which serves
%%as a landscape (Figure~\ref{fig|l2torexample}). The robot instructions are
%%based on pedagogical strategies to promote spatial relation learning by object
%%manipulation. Such instructions include commands to place the elephant
%%\textit{on top} or \textit{next to} the cube, or put the giraffe
%%\textit{inside} the house.  To assess the performance, the robot and the
%%operator need to compute spatial relationships between objects from the visual
%%perspective of the participant.
